---
title: "`r params$title`"
format:
  html:
    toc: false
    css: ["style.css"]
    mainfont: Theinhardt
    fontsize: "16px"
    # To use instead of self-contained that has been deprecated
    embed-resources: true
    # Using custom page layout (via 'style.css')
    page-layout: custom
    # Open link in a new window by default
    link-external-newwindow: false
    # Display footnotes in pop-up window when hovering on it
    footnotes-hover: true
# The empty params are replaced by those passed to "execute_params" when
# rendering
params:
  title: ""
  publication_date: ""
  lang: "en"
  doi: ""
  github_url: ""
editor_options: 
  chunk_output_type: console
---

```{r general-setup, include=FALSE}

## This file contains the ENGLISH version of the data story

# Set general chunk options
knitr::opts_chunk$set(
  echo = FALSE, fig.showtext = TRUE, fig.retina = 3, fig.align = "center",
  warning = FALSE, message = FALSE,
  dev = "svg"
)

# Install snf.datastory package if not available, otherwise load it
if (!require("snf.datastory")) {
  if (!require("devtools")) {
    install.packages("devtools")
    library(devtools)
  }
  install_github("snsf-data/snf.datastory")
  library(snf.datastory)
}

# Load packages
library(tidyverse)
library(lubridate)
library(scales)
library(conflicted)
library(jsonlite)
library(here)
library(glue)
library(ggiraph)
library(showtext)
library(systemfonts)
library(snf.datastory)
library(magrittr)

# Conflict preferences
conflict_prefer("filter", "dplyr")
conflict_prefer("get_datastory_theme", "snf.datastory")
conflict_prefer("get_datastory_scheme", "snf.datastory")

is_theinhardt_available <- file.exists(here("fonts", "TheinhardtReg.otf"))

if (is_theinhardt_available) {
  
  sysfonts::font_add(
    family = "Theinhardt",
    regular = here("fonts", "TheinhardtReg.otf"),
    bold = here("fonts", "TheinhardtBold.otf"),
    bolditalic = here("fonts", "TheinhardtBoldIt.otf"),
    italic = here("fonts", "TheinhardtRegIt.otf"),
  )
  
  # Need to register the font to allow its use by ggiraph when creating SVG
  # files.
  if (!font_family_exists("Theinhardt")) {
    
    # Register existing/downloaded fonts
    register_font(
      name = "Theinhardt",
      plain = list("fonts/TheinhardtReg.otf", 0),
      bold = list("fonts/TheinhardtBold.otf", 0),
      italic = list("fonts/TheinhardtRegIt.otf", 0),
      bolditalic = list("fonts/TheinhardtBoldIt.otf", 0)
    )
  }
  
  font <- "Theinhardt"
  
} else {
  
  font <- "Arial"
  
}

# Need if we want to use the registered font in ggiraph plots
showtext_auto()

# Increase showtext package font resolution
showtext_opts(dpi = 320)

# Set the locale for date formatting (Windows)
Sys.setlocale(
  "LC_TIME",
  switch(
    params$lang,
    en = "English",
    de = "German",
    fr = "French"
  )
)

# Create function to print number with local language-specific format
print_num <- function(x) snf.datastory::print_num(x, lang = params$lang)

# Knitr hook for local formatting of printed numbers
knitr::knit_hooks$set(
  inline <- function(x) {
    if (!is.numeric(x)) {
      x
    } else {
      print_num(x)
    }
  }
)

# Function that returns the desired language version of a string, given three
# language strings are provided to the function.
translate <- function(en_string = "NOT TRANSLATED",
                      de_string = "NOT TRANSLATED",
                      fr_string = "NOT TRANSLATED",
                      lang = "en") {
  
  string <-
    case_when(
      lang == "en" ~ en_string, 
      lang == "de" ~ de_string, 
      lang == "fr" ~ fr_string, 
      TRUE ~ "NO VALID LANGUAGE SPECIFIED"
    )
  
  return(string)
  
}

```

```{r print-header-infos}
#| results: asis

# Add publication date to header
cat(format(as_datetime(params$publication_date), "%d.%m.%Y"))
```

```{r story-specific-setup}
#| include: false

# Set story-specific variables etc. here

input_dir <- "data"

surveys <- read_csv(here(input_dir, "data.csv"),
                    show_col_types = FALSE)

# Plot helper functions

default_levels <- c("No assessment possible",
                    "Completely inaccurate",
                    "Rather inaccurate",
                    "Rather accurate",
                    "Very accurate")

comparison_df <- function(df, column, lvls = default_levels) {
  df %>%
    select(run, question = all_of(column)) %>%
    filter(!is.na(question),
           !question == "") %>%
    mutate(question = str_replace(question, "Prof", "prof"),
           question = str_replace(question, ", namely:", ""),
           question = factor(question,
                             levels = lvls)) %>%
    count(run, question) %>%
    pivot_wider(names_from = run, values_from = n, values_fill = 0) %>%
    mutate(`1 year after the grant` = `1`/sum(`1`),
           `5 years after the grant` = `2`/sum(`2`)) %>%
    select(-c(`1`, `2`)) %>%
    pivot_longer(cols = c(`1 year after the grant`,
                          `5 years after the grant`)) %>%
    mutate(name = name %>% factor(levels = c("5 years after the grant",
                                             "1 year after the grant")))
}

comparison_transl <- function(df) {
  df %>%
    mutate(name = name %>%
             recode("1 year after the grant" =
                      translate("1 year after the grant",
                                "1 Jahr nach der Förderung",
                                "1 an après la fin du subside",
                                params$lang),
                    "5 years after the grant" =
                      translate("5 years after the grant",
                                "5 Jahre nach der Förderung",
                                "5 ans après la fin du subside",
                                params$lang)),
           question = question %>%
             recode("Other position" =
                      translate("Other position", "Andere Position", "Autre",
                                params$lang),
                    "Scientific collaborator" =
                      translate("Scientific collaborator",
                                "Wissenschaftliche Mitarbeit",
                                "Collaboratrice ou collaborateur scientifique",
                                params$lang),
                    "Assistant" =
                      translate("Assistant", "Assistenz", "Assistant·e",
                                params$lang),
                    "Postdoc" =
                      translate("Postdoc", "Postdoktorand:in",
                                "Postdoctorant·e", params$lang),
                    "Lecturer" =
                      translate("Lecturer", "Dozentenstelle",
                                "Chargé·e de cours", params$lang),
                    "SNSF professor" =
                      translate("SNSF professor", "SNF-Förderungsprofessur",
                                "Professeur·e FNS", params$lang),
                    "Assistant professor (without tenure track)" =
                      translate("Assistant professor (without tenure track)",
                                "Assistenzprofessur (ohne Aussicht auf Festanstellung)",
                                "Professeur·e assistant·e (hors prétitularisation conditionnelle)",
                                params$lang),
                    "Assistant professor (with tenure track)" =
                      translate("Assistant professor (with tenure track)",
                                "Assistenzprofessur (mit Aussicht auf Festanstellung)",
                                "Professeur·e assistant·e (en prétitularisation conditionnelle)",
                                params$lang),
                    "Associate professor" =
                      translate("Associate professor",
                                "Ausserordentliche Professur",
                                "Professeur·e associé·e", params$lang),
                    "Full professor" =
                      translate("Full professor",  "Ordentliche Professur",
                                "Professeur·e titulaire", params$lang),
                    "No assessment possible" =
                      translate("No assessment", "Weiss nicht",
                                "Ne se prononce pas", params$lang),
                    "Completely inaccurate" =
                      translate("Completely inaccurate",
                                "Trifft überhaupt nicht zu",
                                "Pas du tout d’accord", params$lang),
                    "Rather inaccurate" =
                       translate("Rather inaccurate", "Trifft eher nicht zu",
                                 "Plutôt pas d’accord", params$lang),
                    "Rather accurate" =
                       translate("Rather accurate", "Trifft eher zu",
                                 "Plutôt d’accord", params$lang),
                    "Very accurate" =
                       translate("Very accurate", "Trifft voll und ganz zu",
                                 "Tout à fait d’accord", params$lang)))
}

comparison_plot <- function(df) {
  df %>%
    ggplot(aes(x = value,
               y = name,
               fill = question)) +
    geom_col(width = .6) +
    geom_text(aes(label = if_else(question %>% as.numeric ==
                                    question %>% as.numeric %>% max,
                                  name %>% as.character, ""),
                  x = 0,
                  y = name %>% as.numeric + 0.5),
              hjust = 0,
              size = 3,
              show.legend = FALSE,
              inherit.aes = FALSE) +
    get_datastory_theme(legend_position = "bottom",
                        legend_margin = ggplot2::margin(l = 7.5, unit = "mm"),
                        family = "Theinhardt",
                        text_axis = "x") +
    scale_fill_manual(values =
                        # Do not use the fourth color: [-4]
                        # Use colors in inverted order
                        get_datastory_scheme()[-4][5:1],
                      guide = guide_legend(reverse = TRUE)) +
    scale_x_continuous(labels = label_percent(accuracy = 1),
                       breaks = c(0, 0.25, 0.5, 0.75, 1))
}
```


<!-- Short lead (2-3 sentences) in bold -->

**The SNSF has been monitoring the impact of Ambizione grants on researchers’
careers via yearly surveys. Grantees highly value the positive effects on their
scientific profile and recognise a career boost.**

Ambizione grants are aimed at mid-career researchers who wish to conduct, manage
and lead an independent project at a Swiss higher education institution.
Afterwards, grantees are expected to either continue on their academic path or
transfer their skills outside academia, in either government or industry. The
Ambizione funding scheme was launched in 2008 and has been running for 15 years,
resulting in the funding of about 1100 researchers in Switzerland. In 2014,
Ambizione was [externally
evaluated](https://www.snf.ch/media/fr/NlJLMmRjkfveCv2f/ambizione_evaluationsbericht_e.pdf).
The evaluation included a survey of grantees to determine the grant’s
implications for their careers. Since then, the SNSF has continued to survey
Ambizione grantees on an annual basis.

In this data story we present a detailed compilation of the results from these
surveys (in relation to the years 2008-2022). Researchers report that Ambizione
has given their career a strong boost. It allowed them to improve their
competences, their scientific profile, their competitiveness, their research
output and their national and international network. While not all Ambizione
grantees were able to gain a foothold in the Swiss research community after a
stay abroad, the vast majority continued to work in research positions after
their grant ended. Five years after the completion of their Ambizione grants,
about three quarters of the grantees hold a professorship position, some in
Switzerland and some abroad.

::: info-box

### Original datasets and cohorts

Every year, the SNSF contacts Ambizione grantees whose grants ended the previous
year. Included are those who completed their grants as well as those who
terminated them early because they found a new position. The grantees are asked
about their Ambizione grant and its impact on their career. We refer to this
group as the “1 year after the grant” cohort. The SNSF also contacts former
Ambizione grantees whose grants ended five years ago. This group is the “5 years
after the grant” cohort. For example, in 2020 the “1 year after the grant”
cohort consisted of former Ambizione grantees whose grants ended in 2019 while
the “5 years after the grant” cohort comprised former Ambizione grantees whose
grants ended in 2015. The response rates are close to 50% for both cohorts.

:::

### Impact on scientific qualification

::: plot-box
::: plot-title
The Ambizione grant has improved my competence in my research field:
:::

```{r improved-competence-plot}
#| out-width: "100%"
#| fig-height: 2

surveys %>%
  comparison_df("improved.competence.in.research.field") %>%
  comparison_transl %>%
  comparison_plot
```

:::

Grantees feel that the Ambizione grant strengthened their research expertise.
The vast majority of them (>95%) reported that their competences have improved
thanks to the Ambizione grant, regardless of whether this was shortly after the
end of the grant or 4 years later.

::: plot-box
::: plot-title
The Ambizione grant has enhanced my scientific profile:
:::

```{r enhanced-profile-plot}
#| out-width: "100%"
#| fig-height: 2

surveys %>%
  comparison_df("enhanced.scientific.profile") %>%
  comparison_transl %>%
  comparison_plot
```

:::

In terms of scientific profile, a vast majority of the Ambizione grantees (>95%)
feel that their scientific profile has been enhanced with the Ambizione grant --
regardless of the cohort.

::: plot-box
::: plot-title
The Ambizione grant has increased my scientific competitiveness:
:::

```{r increased_competitiveness-plot}
#| out-width: "100%"
#| fig-height: 2

surveys %>%
  comparison_df("increased.scientific.competitiveness") %>%
  comparison_transl %>%
  comparison_plot
```

:::

Overall, Ambizione grantees agree that their scientific competitiveness has
increased with the grant. Both cohorts show similar results, with only a
minority of the grantees (<10%) doubting the effects of the Ambizione grant on
their scientific competitiveness.

### Impact on the track record

::: plot-box
::: plot-title
The Ambizione grant has increased the number of my scientific publications:
:::

```{r increased-publications-plot}
#| out-width: "100%"
#| fig-height: 2

surveys %>%
  comparison_df("increased.number.of.scientific.publications") %>%
  comparison_transl %>%
  comparison_plot
```

:::

The Ambizione grant appears to have a positive effect on the grantees’
productivity, resulting in a larger number of publications. However, regardless
of the cohort the data are less clearcut, with 50-60% of the grantees strongly
acknowledging this observation while 30-40% of the grantees only partially
approve it. Nevertheless, only a minority of the grantees (15-20%) questions the
impact of the grant on their research output.

::: plot-box
::: plot-title
The Ambizione grant has improved the quality of my scientific publications:
:::

```{r improved-publication-quality-plot}
#| out-width: "100%"
#| fig-height: 2

surveys %>%
  comparison_df("improved.quality.of.scientific.publications") %>%
  comparison_transl %>%
  comparison_plot
```

:::

Most grantees of both cohorts (75-80%) feel that the quality of their scientific
publications has improved thanks to their Ambizione grant. Nevertheless, the
grantees have mixed feelings about the intensity of these positive effects, with
a minority of them (<20%) expressing doubts about the grant’s impact on the
quality of their publications -- regardless of the cohort.

### Impact on the collaboration network

::: plot-box
::: plot-title
The Ambizione grant has improved my international networking:
:::

```{r improved-networking-plot}
#| out-width: "100%"
#| fig-height: 2

surveys %>%
  comparison_df("improved.networking") %>%
  comparison_transl %>%
  comparison_plot
```

:::

Most of the grantees in both cohorts (75-80%) think that the grant positively
impacted the development of their international network. However, the results
are not clearcut, with 35-40% of the grantees strongly acknowledging the effects
and 35-50% partially acknowledging them. Only 3% of the grantees did not
feel any effect of the Ambizione grant on their international network --
regardless of the cohort.

::: plot-box
::: plot-title
The Ambizione grant has given me easier access to leading scientists in my
research field:
:::

```{r leading-scientist-access-plot}
#| out-width: "100%"
#| fig-height: 2

surveys %>%
  comparison_df("easier.access.to.leading.scientists") %>%
  comparison_transl %>%
  comparison_plot
```

:::

In both cohorts, most grantees (70-75%) feel that the Ambizione grant gave them
access to leading scientists in their research field. However, only 30% strongly
approve this statement, whereas 40-45% of the grantees partially agree with it.
About 25% of the grantees of both cohorts feel that Ambizione did not give them
easier access to leading scientists in their research field.

::: plot-box
::: plot-title
The Ambizione grant has enabled me to gain a foothold in the Swiss science
community after a stay abroad:
:::

```{r return-swiss-science-scene-plot}
#| out-width: "100%"
#| fig-height: 2

surveys %>%
  comparison_df("enabled.to.return.to.swiss.science.scene") %>%
  comparison_transl %>%
  comparison_plot
```

::: caption
Until 2012, applicants had to complete a stay abroad before applying for an
Ambizione grant. From 2012 to 2020, applicants had to complete a stay at a
different research institution from that of their PhD before applying.
:::

:::

Whether the Ambizione grant enables researchers to gain a foothold in
Switzerland after a stay abroad is less clear for both cohorts. In the cohort
“1 year after the grant”, about 50% of the grantees think that their grant
helped them integrate into the Swiss research environment while 25% of the
grantees disagree. Interestingly, 25% of the grantees cannot say if the
Ambizione grant was useful in helping them to access the Swiss science
community.

In the “5 years after the grant” cohort, more Ambizione grantees (approx. 55%)
are positive about the impact the grant had on their entry into the Swiss
science community. However, there are also more grantees (30%) who feel that the
Ambizione grant did not help them much in gaining a foothold in the community.
As in the “1 year after the grant” cohort, many grantees (about 20%) could not
determine if the Ambizione grant helped them to achieve this goal.

### Impact on the career

::: plot-box
::: plot-title
What is your current position?
:::

```{r current-position-plot}
#| out-width: "100%"
#| fig-height: 3

current_position_lvls <- c("Other position",
                           "Scientific collaborator",
                           "Assistant",
                           "Postdoc",
                           "Lecturer",
                           "SNSF professor",
                           "Assistant professor (without tenure track)",
                           "Assistant professor (with tenure track)",
                           "Associate professor",
                           "Full professor")

surveys %>%
  comparison_df("current.position", lvls = current_position_lvls) %>%
  comparison_transl %>%
  comparison_plot +
  scale_fill_manual(values = get_datastory_scheme()[-4][10:1],
                    guide = guide_legend(reverse = TRUE, ncol = 2))
```

:::

The kind of position that grantees have after an Ambizione grant is highly
diverse in both cohorts. Regardless of the cohort, a large majority of the
Ambizione grantees (80-85%) remained in the academic world, either at the level
of professor or researcher/scientific collaborator. Only a minority (15-20%
“Other position”) took a job outside of academia, mostly in industry, government
or teaching.

In the “1 year after the grant” cohort, about 55% of the Ambizione grantees held
a position at the professorial level, mainly as assistant professor, SNSF
professor or lecturer (about 45%). About 25% of the grantees were either
postdoctoral researchers, assistants or scientific collaborators.

In the “5 years after the grant” cohort, about 70% of the Ambizione grantees had
found a position at the professorial level, 40% of the grantees held a position
as full or associate professor and 30% a position as assistant professor, SNSF
professor or lecturer. 5% held a position such as postdoctoral researcher,
assistant or scientific collaborator.

### Diverse positive effects

In conclusion, Ambizione recipients highly value the positive effects of the
grant on their scientific profile, particularly in terms of improving their
competences, their research output, their competitiveness and their
collaboration network. In general, they recognised a boost to their career --
regardless of their cohort and their subsequent position.

Data, text and code of this data story are [available on Github](`r params$github_url`) and [archived on Zenodo](`r params$doi`). <br>DOI: `r str_remove(params$doi, "https://doi.org/")`

```{r prevent-internal-snsf-packages, include=FALSE}
#| include: false

# Internal SNSF packages must not be used in data stories, as their
# pre-processing functions are internal and the corporate design differs from
# the data portal.
if (any(c("snfverse", "snf.preprocessing", "snf.plot") %in% 
        loadedNamespaces())) {
  stop(glue(
    "You must not use internal SNSF packages in data stories.",
    " Please resort to snf.datastory."
  ))
}
```
